Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
important notes

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ for
different sets of faults as to better understand the performance of
\combpar{k}. On the left-hand-side, we show distributions of
$\Delta{}C$, for different values of $k$, considering all cases where
the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
\numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
(see Figure~\ref{fig:diagnosis}). The boxplots on the right-hand-side
of the figure considers all the cases where the predicate
$\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
the cases of faults where the techniques perform equally.\Mar{sofia,
  are you sure there are no zeros in this dataset? The min. in this
  distibution (as per the base of the plot) seems to be 0.} To sum,
although we observed a relatively small number cases where $\Delta{}C$
is negative (\numOutPerformed) and a high number of cases $\Delta{}C$
is zero (\numEquallyPerformed), we observed that there is a
considerable amount of cases where the use of \combpar{k} would be
very beneficial.

>>>>

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ for
different sets of faults as to better understand the performance of
\combpar{k}. 
\Sof{This is not correct}
On the left-hand-side, we show distributions of
$\Delta{}C$, for different values of $k$, considering all cases where
the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
\numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
(see Figure~\ref{fig:diagnosis}). The boxplots on the right-hand-side
of the figure considers all the cases where the predicate
$\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
the cases of faults where the techniques perform equally.\Sof{Needs to be reverted}
\Mar{sofia,
  are you sure there are no zeros in this dataset? The min. in this
  distibution (as per the base of the plot) seems to be 0.}\Sof{Yes, check hangouts} To sum,
although we observed a relatively small number cases where $\Delta{}C$
is negative (\numOutPerformed) and a high number of cases $\Delta{}C$
is zero (\numEquallyPerformed), we observed that there is a
considerable amount of cases where the use of \combpar{k} would be
very beneficial.
